---
title: "test_2"
output: html_document
date: "2023-09-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading the required packages

```{r}
packages = c('tidyverse','ggdist','gghalves','ggthemes','hrbrthemes','ggridges','patchwork','zoo', 'ggrepel','ggiraph','lubridate','gganimate','scales', 'plotly','treemap', 'sf', 'rnaturalearth', 'rnaturalearthdata', 'leaflet', 'trelliscopejs')
for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}

```

### Loading the Dataset


```{r}
malaria_deaths <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-13/malaria_deaths.csv")
malaria_deaths_age <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-13/malaria_deaths_age.csv")
malaria_inc <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-13/malaria_inc.csv")
summary(malaria_deaths)
summary(malaria_deaths_age)
summary(malaria_inc)

```

### Loading a world map, creating world map data with malaria deaths table


```{r}
world_map <- ne_countries(scale = "medium", returnclass = "sf")

world_map_data_with_malaria_deaths <- merge(world_map, malaria_deaths, by.x = "name", by.y = "Entity", all.x = TRUE)
```

### Visualizing the current (i.e. 2016) deaths caused by Malaria on a country level basis


```{r}

world_map_data_with_malaria_deaths_2016 <- world_map_data_with_malaria_deaths %>%
  filter(Year == 2016) %>%
  filter(!is.null(Code)) %>%
  select(name, `Deaths - Malaria - Sex: Both - Age: Age-standardized (Rate) (per 100,000 people)`, Year)
map <- leaflet(world_map_data_with_malaria_deaths_2016) %>%
  addTiles() %>%
  addPolygons(
    fillColor = ~colorFactor("Reds", `Deaths - Malaria - Sex: Both - Age: Age-standardized (Rate) (per 100,000 people)`)(`Deaths - Malaria - Sex: Both - Age: Age-standardized (Rate) (per 100,000 people)`),
    fillOpacity = 0.7,
    color = "white",
    weight = 1,
    popup = ~paste(name, "<br>deaths by malaria per 100,000 people in 2016: ",`Deaths - Malaria - Sex: Both - Age: Age-standardized (Rate) (per 100,000 people)` )
  ) %>%
  setView(lng = 0, lat = 0, zoom = 2)  

map
```

### Create a plotly plot to visualize deaths caused by malaria over the years
```{r}

ggplot_data <- world_map_data_with_malaria_deaths %>%
  filter(!is.null(Code)) %>%
  ggplot(aes(x = Year, y = `Deaths - Malaria - Sex: Both - Age: Age-standardized (Rate) (per 100,000 people)`, color = name)) +
  
  # Add a line plot
  geom_line() +
  
  # Customize the plot
  labs(
    title = "Deaths caused by Malaria per 100,000 people by Country over the years",
    x = "Date",
    y = "Cases",
    color = "Country"
  ) +
  
  # Facet the plot by Region
  facet_wrap(~region_wb, ncol = 2) +
  
  # Improve the aesthetics
  theme_minimal() +
  
  # Rotate x-axis labels for better readability
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

# Convert the ggplot object to a plotly object
plotly_data <- ggplotly(ggplot_data)

# Display the interactive plot
plotly_data
```


### Create a plot using trelliscopejs to visualize deaths caused by malaria by age group and country over the years
```{r}

ggplot_data2 <- malaria_deaths_age %>%
  filter(code != 'NA') %>%
  filter(entity != "World") %>%
  filter(deaths != 0) %>%
  ggplot(aes(x = year, y = deaths, fill = age_group)) + 
  geom_bar(position = "stack", stat="identity") +
  labs(x = 'Year', y= 'Deaths caused by Malaria', title = 'Yearly deaths caused by Malaria by age group') +
  facet_trelliscope(~entity,
                    nrow = 2,
                    ncol = 2,
                    width = 800,
                    self_contained=TRUE) 

ggplot_data2
  
 
```


